\begin{thebibliography}{9}
\bibitem{ddos_forensics} 
Rana Khattak, Shehar Bano, Shujaat Hussain, Zahid Anwar. 
\\\textit{DOFUR: DDoS Forensics Using mapReduce}. Frontiers of Information Technology, 2011.

\bibitem{wireshrk_pcap}
Wireshark Wiki, Development. Last access \textit{May 15 2019}.
\\\url{https://wiki.wireshark.org/Development/LibpcapFileFormat}

\bibitem{detection_by_path_analaysis}
Theerasak Thapngam, Shui Yu, Wanlei Zhou, S. Kami Makki.
\\\textit{Distributed Denial of Service (DDoS) detection by traffic pattern analysis}.
Springer Science, 2012.

\bibitem{ddos_forensics}
Yinghua Guo, Ivan Lee.
\\\textit{Forensic analysis of DoS attack traffic in MANET}. 
Fourth International Conference on Network and System Security, 2010.

\bibitem{memcached_vulnerability}
Cloudflare Inc. Last access \textit{May 30 2019}
\\\textit{An article discussing Memcached UDP Flood vulnerability}. 
\\\url{https://www.cloudflare.com/learning/ddos/memcached-ddos-attack/}

\bibitem{pig_wiki}
Apache.org Last access \textit{May 30 2019}
\\\url{https://cwiki.apache.org/confluence/display/PIG}

\bibitem{jimmy_lin}
Jimmy Lin, Chris Dyer.
\\\textit{Data-Intensive Text Processing with MapReduce}, January 27, 2013.
\\\url{https://github.com/lintool/MapReduceAlgorithms}

\bibitem{proj_repo}
Cristian Turetta, Andrea Perazzoli.
\\\textit{DDoS Network Flow Forensics Analyser}, Github
\\\href{https://github.com/CristianTuretta/DDoS-Network-Flow-Forensics-Analyser-.git}{github.com/CristianTuretta/DDoS-Network-Flow-Forensics-Analyser-.git}

\end{thebibliography}